Verifying Demonstrations

### 2019-02-05 paper/MANETs.tex

%@sbuc: Can you write a few words about MANETs (file MANETs.tex)?
%More specifically, why we can assume there is a way for the
%protesters to communicate locally at the protest without relying on the
%Internet. Also mention potential privacy problems at this layer, e.g.\
%MAC-address tracking etc. which is outside of our protocol (this should
%cover part of issue #58).

Since the cellular network could be shut down to keep protesters from accessing the Internet, making phone calls or texting, we require a different means of communications between protesters. 
This could be accomplished by Bluetooth or WiFi communications, as demonstrated by Briar~\cite{Briar} and FireChat~\cite{FireChat}, two examples of applications for communication during protests via wireless mesh networking. The crowd-counting scenario likely has higher requirements on capacity and withstanding interference as the participants continuously run the protocol for witnessing each others presence; messages are presumably less frequent. 5G is intended to cope with billions of devices (IoT), and thus could help cope with the device density in crowds.
An alternative, although originally designed to work within 5G cellular networks, is device-to-device communication (D2D)~\cite{D2D}. 
Specifically, the out-of-band and autonomous version D2D fits our scenario thanks to using unlicensed spectrum and working without cellular coverage.

>>>>

We also need the participants to communicate during the protest.
Since the cellular network could be shut down to keep protesters from accessing 
the Internet, making phone calls or texting, we require a different means of 
communications between protesters. This could be accomplished by Bluetooth or 
WiFi communications, as demonstrated by Briar~\cite{Briar} and 
FireChat~\cite{FireChat}, two examples of applications for communication during 
protests via wireless mesh networking. The crowd-counting scenario likely has 
higher requirements on capacity and withstanding interference as the 
participants continuously run the protocol for witnessing each others presence; 
messages are presumably less frequent. 5G is intended to cope with billions of 
devices (IoT), and thus could help cope with the device density in crowds.
An alternative, although originally designed to work within 5G cellular networks, is device-to-device communication (D2D)~\cite{D2D}. 
Specifically, the out-of-band and autonomous version D2D would fit our
scenario thanks to using unlicensed spectrum and working without
cellular coverage. Due to the requirements of lawful intercept and the
drive for operators to identify the network users, there still is an
authorization step to communicate in this mode.
%~\footnote{ https://portal.3gpp.org/desktopmodules/Specifications/SpecificationDetails.aspx?specificationId=840}

### 2019-02-05 paper/privacy-analysis.tex

>>>>

Overall, informally, the digital trace needed for verifiability in \CROCUS could
conceivably be used to strengthen a suspicion of
participation.
Given \cref{deanonymizing-storage-adversary} (Grace's) inferences from 
auxiliary information that points
to Alice having participated in a protest, \eg pictures at the
event, with face recognition and subsequent identification, IP address
of her home router, \etc, then any remaining uncertainty from false
positives could be reduced by learning from data on the ledger and
Alice's smartphone. %This potential difference can thus be considered
                    %the price for verifiability.
For confirmation of that suspicion, Grace would have to get access to
and use Alice's private key.

### 2019-02-05 paper/trust-assumptions.tex

\paragraph{ID issuer} We assumed a trusted third party issued certified IDs to every participant (protesters and witnesses). This hypothesis is important to avoid Sybil attacks,
but only the side protesting (not the side being protested against) has an incentive to perform a Sybil attack.
So in practice, the ID issuer doesn't need to be a trusted 3rd-party, it only needs to not be aligned with the protesters.
In our authoritarian government scenario for instance, the protesters can use IDs issued by said government.
On the other hand however, a pro-government protest cannot use the same IDs and offer a good level of trust in the final count, and it would be better suited to use IDs from a different source
(e.g. a supra-national issuer like the EU).

 \paragraph{Verifier's trust in the count} We proposed a generic way of counting, that relies on two parameters: the strength function and the threshold.
%We then suggested two possible instantiations: every witness is equal and we use a relatively large threshold, or we only trust a minority of independent witnesses with a threshold of 1.
An important point here is that these parameters can be chosen by each verifier independently, so each verifier can make choices that satisfy \emph{their} own level of trust, and can each obtain a different final count, and \CROCUS does not output one definitive answer. The trust in a final count depends only on the trust between the verifier and the witnesses.

@@

\paragraph{Protesters and witnesses} Active participants in a protest do not need to trust anything other than that their app is behaving properly and that their smartphone is not compromised. Indeed, \CROCUS has been designed with their privacy and security as a central concern, and being able to use \CROCUS without any additional risk compared to simply come at the protest was one of our main requirement.

>>>>

\subsection{ID issuer} We assumed a trusted third party issued certified IDs to every participant (protesters and witnesses). This hypothesis is important to avoid Sybil attacks,
but only the side protesting (not the side being protested against) has an incentive to perform a Sybil attack.
So in practice, the ID issuer doesn't need to be a trusted 3rd-party, it only needs to not be aligned with the protesters.
In our authoritarian government scenario for instance, the protesters can use IDs issued by said government.
On the other hand however, a pro-government protest cannot use the same IDs and offer a good level of trust in the final count, and it would be better suited to use IDs from a different source
(e.g. a supra-national issuer like the EU).

 \subsection{Verifier's trust in the count} We proposed a generic way of counting, that relies on two parameters: the strength function and the threshold.
%We then suggested two possible instantiations: every witness is equal and we use a relatively large threshold, or we only trust a minority of independent witnesses with a threshold of 1.
An important point here is that these parameters can be chosen by each verifier independently, so each verifier can make choices that satisfy \emph{their} own level of trust, and can each obtain a different final count, and \CROCUS does not output one definitive answer. The trust in a final count depends only on the trust between the verifier and the witnesses.

@@

\subsection{Protesters and witnesses} Active participants in a protest do not need to trust anything other than that their app is behaving properly and that their smartphone is not compromised. Indeed, \CROCUS has been designed with their privacy and security as a central concern, and being able to use \CROCUS without any additional risk compared to simply come at the protest was one of our main requirement.
